### 2013-12-29 prostate_anatomy.tex
minor edits

The prostate gland can be divided from superior-to-inferior into the base,
mid-gland and apex. The urethra enters the prostate proximally at the base and
extends to the mid-gland, at which point the ejaculatory ducts open into the
urethra at the verumontanum.~\cite{Jung2012} The urethra then continues past
the apex and travels through the penis. The prostate can be divided into
glandular and non-glandular components.  The glandular components include the
transitional zone (TZ), central zone (CZ) and peripheral zone (PZ). In the
healthy prostate, each zone contains approximately 5\%, 20\% and 70--80\% of
glandular tissue, respectively.~\cite{Bonekamp2011} The non-glandular
components include the anterior fibromuscular stroma (AFS) and the urethra.  In
some imaging modalities, the central and transition zones cannot be visualized
as discrete entities, and they are collectively identified as the central gland
(CG).  This CG was one of the prostate structures manually segmented in MR and
ARFI images in this study.

>>>>

The prostate gland can be divided from superior-to-inferior into the base,
mid-gland and apex. The urethra enters the prostate proximally at the base and
extends to the mid-gland, at which point the ejaculatory ducts open into the
urethra at the verumontanum.~\cite{Jung2012} The urethra then continues past
the apex and travels through the penis. The prostate can be divided into
glandular and non-glandular components.  The glandular components include the
transitional zone (TZ), central zone (CZ) and peripheral zone (PZ). In the
healthy prostate, each zone contains approximately 5\%, 20\% and 70--80\% of
glandular tissue, respectively.~\cite{Bonekamp2011}, but these ratios can
change significantly in the presence of benign prostatic hyperplasia (BPH). The
non-glandular components include the anterior fibromuscular stroma (AFS) and
the urethra.  In some imaging modalities, the central and transition zones
cannot be visualized as discrete entities, and they are collectively identified
as the central gland (CG).  This CG was one of the prostate structures manually
segmented in MR and ARFI images in this study.
